Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-02 paper.tex
got rid of first paragraph

Imagine an agent faced with a suite of new problems totally different
from anything it has seen before. It has at its disposal a basic set
of primitive actions it can compose to build solutions to these problems, but
it is no idea what kinds of primitives are appropriate for which
problems nor does it know the higher-level vocabulary in
which solutions are best expressed.
How can our agent get off the ground?

>>>>

%% Imagine an agent faced with a suite of new problems totally different
%% from anything it has seen before. It has at its disposal a basic set
%% of primitive actions it can compose to build solutions to these problems, but
%% it is no idea what kinds of primitives are appropriate for which
%% problems nor does it know the higher-level vocabulary in
%% which solutions are best expressed.
%% How can our agent get off the ground?
